---
title: "Kel.1_Kopi Kenangan"
author: "Deswina, Abhie, Wahid"
date: '2022-07-05'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
library(lubridate)
library(dplyr)
library(googlesheets4)
library(tidyverse)
```
```{r}
#Read the Excel data and put it into variable named Follower.
follower <- read_xlsx("Data/IG Follower Scraping.xlsx")

#Read the Excel data and put it into variable named Post.
post <- read_xlsx("Data/IG post Scraping.xlsx")
```

#Check the Head of the Follower data.
```{r}
head(post)
```

### Transform the Post Data


#Try to count the total post of every brands and grouping by Name.
```{r}
post %>% 
  group_by(Name) %>% 
  count(name = "Total Post") %>% 
  arrange(Name)
```

#Try to filter the data based on name "Kopi Kenangan".
```{r}
df_post <- post %>% 
  filter(Name == "Kopi Kenangan")
```

#Try to count the total data based on name "Kopi Kenangan".
```{r}
df_post %>% 
  group_by(Name) %>% 
  count(name = "Total Post")
```

## Cleansing Data

#Convert Date into GMT +7
```{r}
df_post %>% 
  mutate(Date = Date + hours(7))
```

#Make New Variables to store the new data and change the Likes and Comment into Engagement.
```{r}
df_post <- df_post %>% 
  select(-Platform) %>% 
  mutate(Engagement = `Likes and Comment` ) %>% 
  select(-`Likes and Comment`)

```

#Select Date and name "Kopi Kenangan", and then insert into df_follower 
```{r}
df_follower <- follower %>% 
  select(Date, `Kopi Kenangan`)
```

#Relocate the full_date position and overwrite the value in the Variable. 
```{r}
ndf_post <- df_post %>% 
  mutate(full_date = Date) %>% 
  relocate(full_date, .after = Date) %>% 
  mutate(Date = date(Date))
 
```

#Group by year. 
```{r}
ndf_post %>% 
  mutate(year = year(Date)) %>% 
  group_by(year) %>% 
  count()
```

#Filter data with only year 2022 data
```{r}
ndf_post <- ndf_post %>% 
  mutate(year = year(Date)) %>% 
  filter(year == "2022") %>% 
  select(-year)
 
```
### Transform the Follower Data


#Make new variable named final_follower and assign it with Follower data consist of Date, name "Kopi Kenangan"
```{r}
 final_follower <- df_follower %>% 
  select(Date, Follower = `Kopi Kenangan`) %>% 
  mutate(Name = "Kopi Kenangan" )
```


#Filter data with only year 2022 data
```{r}
final_follower <- final_follower %>% 
  mutate(tahun = year(Date)) %>% 
  filter(tahun == "2022") %>% 
  select(-tahun)
```

#Check Missing Value
```{r}
sapply(ndf_post, function(x) sum(is.na(x)))

```
#Check Duplicates
```{r}
sum(duplicated(ndf_post))
```

#summary ndf_post
```{r}
summary(ndf_post)
```

#Add String to the Links with "media/size=l"
```{r}
ndf_post <- ndf_post %>% 
  mutate(Image = paste(Link, "media?size=l", sep = "")) 
```

#Make new variable named Different that comes from the difference of followers per day
```{r}
final_follower <- final_follower %>% 
  mutate(`Different` = `Follower`-lag(`Follower`))
```

### Analyze


# Time (Hours) of Posting With the Highest Average Engagement
```{r}
ndf_post <- ndf_post %>% 
  mutate(Hour = hour(full_date)) 


ndf_post %>% 
  group_by(Hour) %>% 
  summarise(total = n(), `Mean Engagement` = mean(Engagement)) %>% 
  arrange(desc(`Mean Engagement`))
```

# Time Background Posts That Have the Highest Average Engagement
```{r}
ndf_post <- ndf_post %>% 
  mutate('Time Background' = ifelse(Hour == 6 | Hour == 7 | Hour == 8 | Hour == 9 | Hour == 10 | Hour == 11,
                                "Morning",
                                ifelse(Hour == 12 | Hour == 13 | Hour == 14 | Hour == 15 | Hour == 16 | Hour == 17, "Afternoon",
                                       ifelse(Hour == 18 | Hour == 19 | Hour == 20 | Hour == 21, "Evening" , 
                                              "Night"))))
ndf_post %>% 
  group_by(`Time Background`) %>% 
  summarise(Total = n(), `Mean engagement` = mean(Engagement), sum(Engagement)) %>% 
  arrange(desc(`Mean engagement`))
```

#Replace one value N/A in the Different column with 0
```{r}
final_follower[is.na(final_follower)] <- 0
```

# The Average Number of Gained Followers Each Day
```{r}
final_follower%>% 
  group_by(Date = weekdays(Date)) %>% 
  summarise(`Different Follower` = mean(Different)) %>% 
  arrange(desc(`Different Follower`))
```

# When  Kopi Kenangan Gained the Most and the Least Number of Followers
```{r}
final_follower%>% 
  group_by(Date) %>% 
  summarise(`Total Different of Follower` = sum(Different)) %>% 
  arrange(desc(`Total Different of Follower`))
```
```{r}
final_follower%>% 
  group_by(Date) %>% 
  summarise(Sum = sum(Different)) %>% 
  arrange(Sum)
```

# The Month Kopi Kenangan Gained the Most Followers
```{r}
final_follower %>% 
  group_by(Month = months(Date)) %>% 
  summarise(`Different Follower` = sum(Different)) %>% 
  arrange(desc(`Different Follower`))
```

#Make new variable named group that comes from grouping caption
```{r}
ndf_post <- ndf_post %>% 
  mutate(Caption = tolower(Caption)) %>% 
  mutate(group = case_when(grepl("giveaway", Caption) ~ "Giveaway",
                           grepl("promo",Caption) ~ "Promo",
                           grepl("cashback",Caption) ~ "Promo",
                           grepl("hemat",Caption) ~ "Promo",
                           grepl("gratis",Caption) ~ "Promo",
                           grepl("potongan",Caption) ~ "Promo",
                           grepl("diskon",Caption) ~ "Promo",
                           grepl("", Caption, ignore.case = TRUE) ~"Others"))
```

# Five Posts with Most Engagements
```{r}
ndf_post %>% 
  summarise(Engagement, Caption, group) %>% 
  arrange(desc(Engagement))
```

# Average of Engagement Reached of Each Post Category
```{r}
ndf_post %>% 
  group_by(group) %>% 
  summarise(total = n(), mean = mean(Engagement), mean(Likes), mean(Comment)) %>% 
  arrange(desc(mean))
```

### Load Data


#Input JSON from API Key.
```{r}
gs4_auth(path = "my_api_key.json")
```

#Assign the Docs into Variable gsheets.
```{r}
gsheet <- gs4_get("https://docs.google.com/spreadsheets/d/1cyMJTmeCQ0nfECnuImJrpO81PM3qmhfBES28cNaTYd8/edit#gid=0")
```

#Put the Data to the Sheets name "Ade" in the test Google Sheets we have.
```{r}
range_write(gsheet,
            ndf_post,
            sheet = "DF_Post")

range_write(gsheet,
            final_follower,
           sheet = "DF_Follower")
```









